From physical principles to ???

### 2016-02-12 2015CompleteDerivation/completeDerivation.tex
Added the basic points for non-relativistic hamiltonian

This model maps very naturally to a topological space. The states are the elements of a set and the physical outcome provides a topology on that set. The fact that two elements of the set can be distinguished requires the space to be Hausdorff. The fact that the potential outcome of a process are countable requires the space to be second countable.

@@

@@

>>>>

This model maps very naturally to a topological space. The states are elements of a set and the physical outcome provides a topology on that set. The fact that two elements of the set can be distinguished requires the space to be Hausdorff. The fact that the potential outcome of a process are countable requires the space to be second countable.

@@

Show countable basis. $\mathcal{c}= \sum\limits_{\mathcal{s} \in \mathcal{S}} a(\mathcal{s}) \mathcal{e}(\mathcal{s})=\sum\limits_{q \in \mathbbm{Q}} a(q) \mathcal{e}(q)$

Uncountable basis does not work. $\mathcal{c}= \int\limits_{q \in \mathbbm{Q}} \rho(q) \mathcal{e}(q)dq$ but $\rho(q')=|\partial _{q}q'|\rho(q)\neq\rho(q)$

% TODO: need to understand a valid notation for composite state as infinite sum. The densities is the coefficient, the basis are are states, what is the differential?

Find smallest object that can have an invariant density. $\mathcal{c}= \int\limits_{T^*\mathbbm{Q}} \rho(q,k) \mathcal{e}(q,k)dq\wedge dk$

\begin{defn}\label{classical_phase_space}
The state space $\mathcal{S}$ for the particles of a homogeneous classical  system is a cotangent bundle $T^*\mathbbm{Q}$.
\end{defn}

\begin{justification}
	TODO
\end{justification}

Density allows to count particle states. Example: two uniform distribution for the same amount of particles.

Area in each d.o.f. is number of possibilities. Total number of states is product of number of possibilities for independent d.o.f. Independent d.o.f. are orthogonal. Leads to omega metric. As in discrete case, conserved during evolution.

Also: we can search for omega looking from constraints. Must be linear. Must be skew-symmetric (applied to the same vector twice must be zero). Must be invariant by coord transformation.

\begin{defn}\label{symplectic_manifold}
	The state space $\mathcal{S}$ for the particles of a homogeneous classical  system is a symplectic manifold with metric $\omega$, the canonical two-form.
\end{defn}

\begin{justification}
	TODO
\end{justification}

@@

\begin{defn}\label{canonical_transformation}
	A deterministic and reversible process is a diffeomorphism that preserves $\omega$, that is a canonical transformation.
\end{defn}

\begin{justification}
	TODO
\end{justification}

\begin{defn}\label{hamiltonian}
	A continuous deterministic and reversible process admits a potential $H$, and the laws of evolution are of the form (Hamilton equations).
\end{defn}

\begin{justification}
	TODO
\end{justification}
